---
title: "Powers package"
author: "Zeid Hamadeh"
date: "`r Sys.Date()`"
output: github_document
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/vincenzocoia/powers)

This is an R package that gives multiple power functions such as `sqrt()`, `log_trans()` and `boxcox()`. You can find the DESCRIPTION, LICENSE and NAMESPACE in this repository. All other relevant documentation can be found in the quick links below.

## Quick links

* [Function packages](https://github.com/STAT545-UBC-students/hw07-zhamadeh/tree/master/R)
* [Function documentation](https://github.com/STAT545-UBC-students/hw07-zhamadeh/tree/master/man)
* [Function tests](https://github.com/STAT545-UBC-students/hw07-zhamadeh/tree/master/tests/testthat)
* [Vignettes](https://github.com/STAT545-UBC-students/hw07-zhamadeh/tree/master/vignettes)


## Installation

You can install powers from github by first installing the `devtools` package and using the `install_github()` method like so:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("STAT545-UBC-students/hw07-zhamadeh")
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example}
powers::log_trans(9,3)
powers::square(16)
powers::cube(3)
```

## For Developers

Use the internal `pow` function as the machinery for the front-end functions such as `square`, `cube`, and `reciprocal`. 
